---
title: "assignment 4"
author: "joshna katta"
date: "2022-10-31"
output:
  html_document: default
  word_document: default
  pdf_document: default
---
```{r}
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
```

```{r}
library("Benchmarking")
```

```{r}

data.df.values <- matrix(c("Facility 1","Facility 2","Facility 3","Facility 4","Facility 5", "Facility 6",
                150,400,320,520,350,320,
                0.2,0.7,1.2,2.0,1.2,0.7,
                14000,14000,42000,28000,19000,14000,
                3500,21000,10500,42000,25000,15000), ncol=5, byrow=F)
colnames(data.df.values) <- c("DMU", "Staff_Hours_Per_Day","Supplies_Per_Day","Reimbursed_Patient_Days","Privately_Paid_Patient_Days")
table.df <- as.table(data.df.values)
table.df
```

***Calculating Constant Returns to Scale (CRS)***
```{r}

x <- matrix(c(150,400,320,520,350,320,
            0.2,0.7,1.2,2.0,1.2,0.7),ncol=2)
y <- matrix(c(14000,14000,42000,28000,19000,14000,
                3500,21000,10500,42000,25000,15000),ncol=2)
colnames(y) <- c("Reimbursed_Patient_Days","Privately_Paid_Patient_Days")
colnames(x) <- c("Staff_Hours_Per_Day","Supplies_Per_Day")
D_E_A_crs<-dea(x, y, RTS = "crs")
D_E_A_crs
peers(D_E_A_crs)
lambda(D_E_A_crs)
```
*CRS Observations -* 
\newline
*1. We get to see that Facility 1, Facility 2, Facility 3  and Facility 4 are efficient.*
\newline
*2. Also, we get to see that Facility 1, Facility 2 and Facility 4 are the peer members for Facility 5 and Facility 6 which are the inefficient facilities.*
\newline
*3. Facility 5 is 97.75 % efficient leaving 2.25 % as inefficient and Facility 6 is 86.75 % efficient leaving 13.25 % as inefficient.*
\newline

***Calculating Decreasing Returns to Scale (DRS)***
```{r}

D_E_A_drs <- dea(x, y, RTS = "drs")
D_E_A_drs
peers(D_E_A_drs)
lambda(D_E_A_drs)
```
*DRS Observations -* 
\newline
*1. We get to see that Facility 1, Facility 2, Facility 3  and Facility 4 are efficient.*
\newline
*2. Also, we get to see that Facility 1, Facility 2 and Facility 4 are the peer members for Facility 5 and Facility 6 which are the inefficient facilities.*
\newline
*3. Facility 5 is 97.75 % efficient leaving 2.25 % as inefficient and Facility 6 is 86.75 % efficient leaving 13.25 % as inefficient.*
\newline


***Calculating Increasing Returns to Scale (IRS)***
```{r}

D_E_A_irs <- dea(x, y, RTS = "irs")
D_E_A_irs
peers(D_E_A_irs)
lambda(D_E_A_irs)
```
*IRS Observations -* 
\newline
*1. We get to see that Facility 1, Facility 2, Facility 3, Facility 4 and Facility 5 are efficient.*
\newline
*2. Also, we get to see that Facility 1, Facility 2 and Facility 5 are the peer members for Facility 6 which is the only inefficient facility.*
\newline
*3. Facility 6 is 89.63 % efficient leaving 10.37 % as inefficient.*
\newline

***Calculating Variable Returns to Scale (VRS)***
```{r}

D_E_A_vrs <- dea(x, y, RTS = "vrs")
D_E_A_vrs
peers(D_E_A_vrs)
lambda(D_E_A_vrs)
```
*VRS Observations -* 
\newline
*1. We get to see that Facility 1, Facility 2, Facility 3, Facility 4 and Facility 5 are efficient.*
\newline
*2. Also, we get to see that Facility 1, Facility 2 and Facility 5 are the peer members for Facility 6 which is the only inefficient facility.*
\newline
*3. Facility 6 is 89.63 % efficient leaving 10.37 % as inefficient.*
\newline

***Calculating Free Disposability Hull (FDH)***
```{r}

D_E_A_fdh <- dea(x, y, RTS = "fdh")
D_E_A_fdh
peers(D_E_A_fdh)
lambda(D_E_A_fdh)
```
*FDH Observations -* 
\newline
*All the DMUs are efficient. This is basically due to the principal which FDH technique follows thereby detecting even a small level of efficiency.*
\newline

***Calculating Free Replicability Hull (FRH)***
```{r}

#here FRH is calculated by specifying RTS = "add"
D_E_A_frh <- dea(x, y, RTS = "add")
D_E_A_frh
peers(D_E_A_frh)
lambda(D_E_A_frh)
```